Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-11-28 manuscript/supplemental_material.Rnw
fix placenta classification plot

\begin{table}[hb]
<<placental_classification_table,echo=FALSE,results="asis">>=
print(xtable(placenta_classification,
             display=c("s","s","s","s","s"),
             align=c("c","c","c","c","c")),
      include.rownames=FALSE,
      floating=FALSE,
      booktabs=TRUE
      )

>>>>

\begin{table}[hb]
<<placental_classification_table,echo=FALSE,results="asis">>=
plac.class <- copy(placenta_classification[,list(species,shape,interdigitation,intimacy)])
plac.class[,`species`:=paste0("\\textit{",gsub("^(.)","\\U\\1",`species`,perl=TRUE),"}")]
plac.class[,`interdigitation`:=gsub("^(.)","\\U\\1",`interdigitation`,perl=TRUE)]
plac.class[,`shape`:=gsub("^(.)","\\U\\1",`shape`,perl=TRUE)]
plac.class[,`intimacy`:=gsub("^(.)","\\U\\1",`intimacy`,perl=TRUE)]
setnames(plac.class,colnames(plac.class),gsub("^(.)","\\U\\1",colnames(plac.class)))

print(xtable(plac.class,
             display=c("s","s","s","s","s"),
             align=c("c","c","c","c","c")),
      include.rownames=FALSE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,
      booktabs=TRUE
      )
